\ab{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}

### 2021-01-17 papers/intro_paper/intro_paper.tex
changes up to Sec. III

In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
latter are related to the BBH's component masses and spins through
NR--fitting-formulas obtained in
GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
spirit of what was done in \paperone, we promote the QNM (complex)
frequencies to be free parameters of the model, while keeping the
inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
to their GR values. \ab{More explicitly, we introduce a parameterized 
version of the $\SEOB$ model where the frequency and the
damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
_{\ell m 0})$) is defined through the fractional deviations, $(\delta
f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,} 
\begin{eqnarray}
f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
\end{eqnarray}
\ab{We denote such a parameterized waveform model \pSEOB}~\footnote{\ab{This 
waveform model is called {\tt pSEOBNRv4HM} in LAL.}}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbt]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}). The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. \comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
	\label{fig:simulated_signal_GR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We find, as one might expect, that the posterior distribution on the
parameters describing fractional deviations in the frequency and
damping time are consistent with zero (left panels of
Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
fractional quantities into absolute quantities using the relations
given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
construct posterior distributions on these effective quantities,
$(\fngr{220}, \taungr{220})$ (right panels of
Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
posterior are consistent with the GR predictions (black \sout{solid lines} \ab{dot}).

@@

To demonstrate the robustness of the method in detecting possible
deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
the corresponding GR prediction up to merger, and differ in their post-merger
description. We again choose \sout{systems with initial-}binary-parameters
similar to GW150914 and GW190521 (as given in Table XXX), but 
\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
\ab{set} $\df{220} = \dtau{220} = 0.5$ \abhi{deviations=0.1 runs are ongoing and almost
  done}. In other words, we assume that the frequency and damping time
of our non-GR signal is 1.5 times the corresponding GR prediction,
although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
you just clearly refer to thePlease introduce the injected signal and the template, which is used 
to recover it, and simply say that they belong to the same waweform model.} 
We also avoid waveform \sout{and noise} systematic biases by choosing 
a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
explaining the results in teh figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}

We additionally investigate the effects of erroneously assuming that
\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
signals using the GR waveform model $\SEOB$ instead of the parameterized 
$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
In such cases, we run the risk of biased parameter estimates due to an
incomplete understanding of the underlying signal. The resulting
posterior probability distributions are shown in the right panels of
Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
(GW190521-like) curves.} The results are interesting and distinctly
different for the two events. For the GW150914-like \comment{AB: I would avoid using 
``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
reported \emph{no} deviation from the GR prediction. However in the
case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
the non-GR signal would have yielded measurements distinctly
different from either of the two parameterized estimates: with and
without deviations. \comment{AB: Not clear to me the next sentence. We are working 
in Gaussian noise, so why are you referring to the noise as the culprit or the 
source of difference?} The fact that the GW190521-like signal has a much
lower SNR than GW150914-like signal might be a possible reason for the 
measurement of the final quantities to be more susceptible to noise. A
more detailed comparison of the other parameters, like the masses and
spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR
signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
comment the figures. What are the main results? What do we deduce?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarisation of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (solid orange lines), i.e., $\df{220} = \dtau{220} = 0$, and where the merger-ringdown is modified (dashed grey lines), i.e., $\df{220} = \dtau{220} = 0.5$. Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and modified GR signal. \comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from teh y-axis labels, but instead provide 
explanations in the caption, and use only $f(t)$.}}
	\label{fig:nongr_waveform}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: non-GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}%[h!]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for modGR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}). The underlying signal has a deviation, $\df{220} = \dtau{220} = XX$. The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. In the right panels, we additionally show measurements using a GR (\SEOB) waveform, for GW150914 (grey) and GW190521 (pink), The measurements are visibly biased. \comment{AB:The labels of the plots on theright are 
wrong, I believe, because otehrwise I don't understand the results. Please rewrite the caption in a more concise and clear way. It is difficult 
to understand it. We are not using the notation ``modGR'' anywhere else in the paper. We don't invent new notations each time!}}
	\label{fig:simulated_signal_nonGR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% modified GR signal: GR vs nonGR recovery comparison
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}%[h!]
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
	\caption{\textcolor{red}{FINAL RESULT} Comparison of the recovered parameters when the underlying signal is assumed to be a GR signal or a modified GR signal. In both cases, the actual underlying signal is a modified GR signal with parameters similar to GW150914 (left panels) and GW190521 (right panels) respectively. The initial parameters are given in Table~\ref{tab:injection_values}, with the QNM parameters defined by $\df{220} = \dtau{220} = 0.5$. For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively. The panels (from top to bottom) show the recoveries in (detector-frame) initial masses (first row), z-components of dimensionless initial spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f, a_f$) from the frequency and damping time (obtained by inverting the Berti fits) CITE}
	\label{fig:gr_ngr_comparison}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, we provide a simple demonstration of a test of the no-hair theorem using our model. As described in the introduction, any test of the no-hair theorem of BHs would need to involve independent measurements of (at least) two different QNMs. We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning BBH with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$ (Table~\ref{tab:injection_values}). We choose an asymmetric system to increase the SNR in the higher modes. We also rescale the distance and orientation of the binary such that the total SNR of the signal in a network of three detectors, LIGO Hanford, Livingston and Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such asymmetric and loud signals are no longer just a theoretical prediction but quite plausible at design sensitivities. Using this signal, we attempt to measure the QNM frequencies $(2,\pm 2)$ and $(3,\pm 3)$ modes together (Fig.~\ref{fig:nohair_sxs}). The SNR in other sub-dominant modes is too less for us to estimate them reliably.

The fractional deviations in the estimates of the damping time and frequency of either mode is expected to be consistent with 0, as we indeed find in the left panel of Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330}, \taungr{330})$  are also consistent with the corresponding predictions for a BBH merger in GR. As a consequence, the information from these two independent measures correspond to a unique remnant object, which is completely described by its mass and spin angular momentum \abhi{have the mf-af plot as well as a third panel to show consistency}. For most of the events observed so far, the power in the $(3,\pm 3)$ has not been sufficient to measure it along with the $(2,\pm 2)$, or in fact, in its place. However, it might also be possible to combine information from multiple observation, as is likely over the coming few years of GW astronomy with the LIGO-Virgo detectors, to obtain meaningful constraints on the $(3,\pm 3)$ and other sub-dominant QNMs.

>>>>

In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
latter are related to the BBH's component masses and spins through
NR--fitting-formulas obtained in
GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
spirit of what was done in \paperone, we promote the QNM (complex)
frequencies to be free parameters of the model, while keeping the
inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
to their GR values. \ab{More explicitly, we introduce a parameterized 
version of the $\SEOB$ model where the frequency and the
damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
_{\ell m 0})$) is defined through the fractional deviations, $(\delta
f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,} 
\begin{eqnarray}
f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
\end{eqnarray}
\ab{We denote such a parameterized waveform model $\pSEOB$}~\footnote{\ab{This 
waveform model is called {\tt pSEOBNRv4HM} in LAL.}}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbt]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}). The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. \comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
	\label{fig:simulated_signal_GR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We find, as one might expect, that the posterior distribution on the
parameters describing fractional deviations in the frequency and
damping time are consistent with zero (left panels of
Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
fractional quantities into absolute quantities using the relations
given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
construct posterior distributions on these effective quantities,
$(\fngr{220}, \taungr{220})$ (right panels of
Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
\ab{2D} posterior{\ab{s} are consistent with the GR predictions 
(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring 
to 1D and 2D posteriors when discussing the figures.}}

@@

To demonstrate the robustness of the method in detecting possible
deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
the corresponding GR prediction up to merger, and differ in their post-merger
description. We again choose \sout{systems with initial-}binary-parameters
similar to GW150914 and GW190521 (as given in Table XXX), but 
\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
  done. AB: I would show results that include the $10\%$ case, which is more realistic, 
based on QNM predictions in theories of gravity alternative to GR.}. 
In other words, we assume that the frequency and damping time
of our non-GR signal is 1.5 times the corresponding GR prediction,
although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
you just clearly refer to thePlease introduce the injected signal and the template, which is used 
to recover it, and simply say that they belong to the same waweform model.} 
We also avoid waveform \sout{and noise} systematic biases by choosing 
a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
explaining the results in teh figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}

We additionally investigate the effects of erroneously assuming that
\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
signals using the GR waveform model $\SEOB$ instead of the parameterized 
$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
In such cases, we run the risk of biased parameter estimates due to an
incomplete understanding of the underlying signal. The resulting
posterior probability distributions are shown in the right panels of
Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
(GW190521-like) curves.} The results are interesting and distinctly
different for the two events. For the GW150914-like \comment{AB: I would avoid using 
``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
reported \emph{no} deviation from the GR prediction. However in the
case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
the non-GR signal would have yielded measurements distinctly
different from either of the two parameterized estimates: with and
without deviations. \comment{AB: Not clear to me the next sentence. We are working 
in Gaussian noise, so why are you referring to the noise as the culprit or the 
source of difference?} The fact that the GW190521-like signal has a much
lower SNR than GW150914-like signal might be a possible reason for the 
measurement of the final quantities to be more susceptible to noise. A
more detailed comparison of the other parameters, like the masses and
spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
comment the figures. What are the main results? What do we deduce?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$). Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal. \comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
	\label{fig:nongr_waveform}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: non-GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}%[h!]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$. The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the 
GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please 
switch the red and blue colors. The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots. Please indicate on the figures: GW150914-like and GW190521-like.}}
	\label{fig:simulated_signal_nonGR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% modified GR signal: GR vs nonGR recovery comparison
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}%[h!]
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
	\caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}. \sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to 
a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time 
(obtained by inverting the Berti fits). \comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption. Also please specify if the remnant mass is the detector-frame mass. Please 
switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
	\label{fig:gr_ngr_comparison}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, we provide a simple demonstration of a test of the no-hair
theorem using our model. As described in the introduction, any test of
the no-hair theorem of BHs would need to involve independent
measurements of (at least) two different QNMs.

\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{} 
corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166), 
\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}). 
We choose an asymmetric system to increase the SNR in the higher modes. 
We also \sout{rescale} \ab{choose} the distance and orientation of the binary 
such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of 
the three detectors, LIGO Hanford, Livingston and
Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
asymmetric and loud signals are no longer just a theoretical
prediction, but quite plausible at design sensitivities. Using this
signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize 
our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}

The fractional deviations in the estimates of the damping time and
frequency of either mode is expected to be consistent with 0, as we
indeed find in the left panel of
Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
\taungr{330})$ are also consistent with the corresponding predictions
for a BBH merger in GR. As a consequence, the information from these
two independent measures correspond to a unique remnant object, which
is completely described by its mass and spin angular momentum
\abhi{have the mf-af plot as well as a third panel to show
  consistency}. For most of the events observed so far, the power in
the $(3,\pm 3)$ has not been sufficient to measure it along with the
$(2,\pm 2)$, or in fact, in its place. However, it might also be
possible to combine information from multiple observation\sout{, as is
likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
other sub-dominant QNMs~\cite{}.
